A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-08-26 rr-flow.Rmd
add (unfinished) setup

>>>>

# Set up Workflow

This workflow directly relies on three software packages: `git`, `make` and `docker`. Of course it depends also indirectly on R, RStudio & RMarkdown, but they do not need to be installed. The installation process depends on the operating system, e.g. on OS X, make is allways availible or on Linux git & make are often allready installed. In the following section we share what have experienced as the easiest options.

## Windows

Windows has the bigest hurdle to install what is needed. However there is a great package manager for Windows called chocolately which you can install from: [https://chocolatey.org](https://chocolatey.org).
After having installed chocolately, all dependencies can be installed in an **admin terminal** via:

```{bash, eval=FALSE}
choc install git make docker-desktop
```
